\vspace{5cm} \normalsize \textsc{\NetIDb} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{\documenttitle}} \HRule{2pt} \\ [0.5cm] \normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\ }\normalsize \vspace*{5\baselineskip}

### 2025-03-25 Manuscript/Plantilla memòria TFG 2024_25.tex
Writting

The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. In this project we do focus on the \gls{ic50}.

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. One of the best drug candidates is

>>>>

The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. Taking advantage of the health interest and the large sets of data, we do focus on the \gls{ic50}. The \gls{ic50} is concentration assigned to the drug concentration required for a $50\%$ inhibition a protein, and is one of the most standard values to compute inhibition potentials as well as \gls{ic90} and \gls{ic99}. The lower the \gls{ic50} of a molecule the lower concentration of the molecule for suppressing the portein (i.e.\gls{cox2}) activity, ergo the molecule inhibits the protein more efficiently. This factor is key when it comes to drug design since a low inhibition potentials implies a low presence of external substances in the organism, a factor that helps to prevent drug's side effects\footnote{Naturally there are plently of other factors related to drug side effects}.

Taking advantage of this

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. One of the best drug candidates is the Celecoxib (Def. (\ref{definitionCelecoxib})) and the Rofecoxib (Def. (\ref{definitionRofecoxib})). The the Physical Chemistry Unit at UAB \cite{UAB_ComputationalChemistry},
